Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-14 ieee_paper.tex
updated plots.
Updated papers to refer to pdf plots and modifed pdf legend positions.

\def\qes#1{}
\def\es#1{}
\def\ge#1{}
%\usepackage{morefloats}

@@

  \subfigure[Bandwidth performance under idealized conditions as a
    function of matrix row size. Entries with "cpp" denote cases where
    coding was performed without MIC vector
    instructions.]{\includegraphics[width=.49\linewidth]{figures/test1_readwrite.png}\label{fig:band_rw}}
%
  \subfigure[Bandwidth performance under
  idealized conditions as a function of matrix row size. Entries with
  "cpp" denote cases where coding was performed without MIC vector
  instructions.]{\includegraphics[width=.49\linewidth]{figures/test1_gather.png}\label{fig:band_gather}}

  \subfigure[Bandwidth performance under idealized conditions as a
    function of matrix row size. Entries with "cpp" denote cases where
    coding was performed without MIC vector instructions. The greater
    speed of the cpp version is obtained throught the use of
    \ttt{\#Ivdep} {\em and\/} \ttt{\_\_assumed\_aligned}. All memory
    is aligned on 64
    bytes.]{\includegraphics[width=.49\linewidth]{figures/test3_gather.png}\label{fig:band_gather_ivdep}}
%
  \subfigure[Bandwidth performance on the host under idealized
    conditions as a function of matrix row size. Entries with "cpp"
    denote cases where coding was performed without AVX vector
    instructions. The speed on the CPU matches the speed with AVX
    instructions. All memory is aligned on 32
    bytes.]{\includegraphics[width=.49\linewidth]{figures/host_test1_readwrite_no_temporal_hint.png}\label{fig:read_write}}

@@

  \subfigure[Performance of $y=Ax$ on the MIC. Squares: base 1/1 case,
    solid circles: 4/4 case implemented in C++, solid triangles: 4/4
    case implemented with MIC vector instructions. $-O3$ compilation
    options. Each group consists of four cases: grids of $64^3$ and
    $96^3$ with and without Reverse Cuthill
    McKee.\todo{I don't think this is supercompact but RBF 3D.}]{\includegraphics[width=.49\linewidth]{figures/mic_performance_nb_threads.png}\label{}}
%
  \subfigure[performance on the host on a 64x64x64 matrix. Manual
    vectoization brings significant improvement there as
    well.]{\includegraphics[width=.49\linewidth]{figures/64x64x64.pdf}\label{}}

>>>>

\def\qes#1{}
\def\es#1{}
%\def\ge#1{}
%\usepackage{morefloats}

@@

  \subfigure[Bandwidth performance under idealized conditions as a
    function of matrix row size. Entries with "cpp" denote cases where
    coding was performed without MIC vector
    instructions.]{\includegraphics[width=.49\linewidth]{figures/test1_readwrite.pdf}\label{fig:band_rw}}
%
  \subfigure[Bandwidth performance under
  idealized conditions as a function of matrix row size. Entries with
  "cpp" denote cases where coding was performed without MIC vector
  instructions.]{\includegraphics[width=.49\linewidth]{figures/test1_gather.pdf}\label{fig:band_gather}}

  \subfigure[Bandwidth performance under idealized conditions as a
    function of matrix row size. Entries with "cpp" denote cases where
    coding was performed without MIC vector instructions. The greater
    speed of the cpp version is obtained throught the use of
    \ttt{\#Ivdep} {\em and\/} \ttt{\_\_assumed\_aligned}. All memory
    is aligned on 64
    bytes.]{\includegraphics[width=.49\linewidth]{figures/test3_gather.pdf}\label{fig:band_gather_ivdep}}
%
  \subfigure[Bandwidth performance on the host under idealized
    conditions as a function of matrix row size. Entries with "cpp"
    denote cases where coding was performed without AVX vector
    instructions. The speed on the CPU matches the speed with AVX
    instructions. All memory is aligned on 32
    bytes.]{\includegraphics[width=.49\linewidth]{figures/host_test1_readwrite_no_temporal_hint.pdf}\label{fig:read_write}}

@@

  \subfigure[Performance of $y=Ax$ on the MIC. Squares: base 1/1 case,
    solid circles: 4/4 case implemented in C++, solid triangles: 4/4
    case implemented with MIC vector instructions. $-O3$ compilation
    options. Each group consists of four cases: grids of $64^3$ and
    $96^3$ with and without Reverse Cuthill
    McKee.\todo{I don't think this is supercompact but RBF 3D.}]{\includegraphics[width=.49\linewidth]{figures/mic_performance_nb_threads.pdf}\label{}}
%
  \subfigure[performance on the host on a 64x64x64 matrix. Manual
    vectoization brings significant improvement there as
    well.]{\includegraphics[width=.49\linewidth]{figures/64x64x64.pdf}\label{}}
